---
title: "Week 1"
author: "Multifaceted"
date: "May 18, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
if (! 'package:tidyverse' %in% search()) library(tidyverse)
```

(a) Make the scatter diagram with sales on the vertical axis and advertising on the horizontal axis. What do you
expect to find if you would fit a regression line to these data?

```{r cars}
data <- read_table2('TestExer-1-sales-round1.txt')
ggplot(data, aes(x = Advert.,y = Sales)) + geom_point()
```

The model will be significantly affected by the outlier point.


(b) Estimate the coefficients a and b in the simple regression model with sales as dependent variable and advertising
as explanatory factor. Also compute the standard error and t-value of b. Is b significantly different from 0?

```{r formula}
md <- lm(Sales~Advert., data = data)
summary(md)
```

a = 29.6  b - -0.325
The standard error of b is 0.459.
The t-value of b is -0.707, which is not significantly different from 0.

(c) Compute the residuals and draw a histogram of these residuals. What conclusion do you draw from this
histogram?

```{r residual}
res <- residuals(md)
res <- tibble(index = 1:length(res), value = res)
ggplot(res, aes(x = value)) + geom_histogram()
```

There is an observation of which the estimation is wrong.

  
(d) Apparently, the regression result of part (b) is not satisfactory. Once you realize that the large residual
corresponds to the week with opening hours during the evening, how would you proceed to get a more
satisfactory regression model?

Delete the outlier point.


(e) Delete this special week from the sample and use the remaining 19 weeks to estimate the coefficients a and
b in the simple regression model with sales as dependent variable and advertising as explanatory factor. Also
compute the standard error and t-value of b. Is b significantly different from 0?

```{r delete outlier}
idx <- which(data$Sales > 30)
newdata <- data[-idx, ]
n_md <- lm(Sales~Advert., data = newdata)
summary(n_md)
```

a = 21.1  b = 0.375 
The standard error of b is 0.0882.
The t-value of b is 4.25, which is significantly different from 0.


(f) Discuss the differences between your findings in parts (b) and (e). Describe in words what you have learned from these results.


e eliminate the effect of outlier. Therefore the result is more reliable. We have to plot the data and remove the outlier before fitting a linear model.